---
title: "iteration_and_listcols"
author: "Kylie Wheelock Riley"
date: "10/29/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set
library(tidyverse)

set.seed(1)
```

## Lists
```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

```{r}
#List is letting us storewhatever we want
#Several ways to access things in list (name $, index[[2]], mean(l, vec_numeric))
l = list(vec_numeric = 5:8,
         mat         = matrix(1:8, 2, 4),
         vec_logical = c(TRUE, FALSE),
         summary     = summary(rnorm(1000)))
l

l$vec_numeric
## [1] 5 6 7 8
l[[1]]
## [1] 5 6 7 8
l[[1]][1:3]
```

##For Loops
```{r}
df = list(
  a = rnorm(20, 3, 1),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)

is.list(df)
```

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

Using function on list
```{r}
mean_and_sd(df[[1]])
mean_and_sd(df[[2]])
mean_and_sd(df[[3]])
mean_and_sd(df[[4]])
```
But now there are a bunch of outputs from the function. Want to store them. Can use for loop. 

Writing our first for loop. 

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(df[[i]])
}

output
```

## Map
Want to change the for loop to a map statement
```{r}
output = map(df, mean_and_sd)

output_median = map(df, median)
##Just mapping median

output_summary = map(df, summary)
##Mapping summary
 
##AFTER CLASS LOOK UP HOW TO GET AN OUTPUT OF A DF< OR A JOINED DF
output_median = map_dbl(df, median)
##putput = map_df(df, ??)
```

More specific arguments
```{r}
output = map_df(.x = df, ~ mean_and_sd(.x))
```

### Map Variants
```{r}
output = map_dbl(df, median, .id = "input")
output = map_dfr(df, mean_and_sd, .id = "input")

```


##Napolean Dynamite Example
```{r}
library(rvest)

read_page_reviews = function(url) {
  
  h = read_html(url)
  
  title = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = h %>%
    html_nodes(".review-data:nth-child(5)") %>%
    html_text()
  
  data_frame(title, stars, text)
}
```

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

output = vector("list", length = 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

dynamite_reviews = bind_rows(output)

dynamite_reviews = map_df(vec_urls, read_page_reviews)

output = (map(vec_urls, read_page_reviews))
```

## List Columns
```{r}
weather = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2016-01-01",
    date_max = "2016-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Nest within station. 
```{r}
weather_nest = 
  weather %>% 
  nest(data = date:tmin)

weather_nest %>% pull(name)
weather_nest %>%  pull(data)

##Looking at first list entry
weather_nest$data[[1]]
```

Unnesting
```{r}
unnest(weather_nest, cols = data)

```

Operations on List Columns
```{r}

#making sure it works on a singular DF
weather_lm(weather_nest$data[[1]])

#weather_data lis a list, can use list_lm
weather_lm(weather_nest$data[[1]])
weather_lm(weather_nest$data[[2]])
weather_lm(weather_nest$data[[3]])
```

...try a loop
```{r}
## double check after class
output = vector("list")
map(weather_nest$data, weather_lm)


weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}
```
adding column
```{r}
weather_nest %>% 
  mutate(lin_models = map(data, weather_lm))
```

Revisitng past examples
```{r}
dynamite_reviews = 
  tibble(page = 1:5,
         urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) %>%
  unnest() %>% 
  select(urls)
```

