---
title: "Writing Functions"
author: "Kylie Wheelock Riley"
date: "10/24/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)

set.seed(1)
```

## Writing Functions:
To write a function, you first need to start with smaller pieces of code that work outside of a function. 

The chunk below takes a sample from a normal distribution and then computes the vector of Z scores for the sample.

```{r}
x = rnorm(n = 30, mean = 4, sd = 2.3)
x_again = rnorm(n = 30, mean = 6, sd = .3)

(x - mean(x)) / sd(x)
(x_again - mean(x_again)) / sd(x_again)
```


If I want to repeat this process for lots of samples, I might want to have a function that takes the sample as an argument, computes the vector of Z scores in the body, and returns the result. I define such a function below.
```{r}
z_scores = function(x_arg) {
  ##adding conditional formatting so the function only works on the type of data you want
    if (!is.numeric(x_arg)) {
    stop("Argument x should be numeric")
  } else if (length(x_arg) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  z = (x_arg - mean(x_arg)) / sd(x_arg)
  z
  
}

z_scores(x)
```

I can try this with a few samples and confirm that it works. I should also try to think of ways this code might break; the attempts below try a variety of inputs to see what happens.
```{r, error = TRUE}
z_scores(x_arg = y)
##figure out what y is after class

z_scores(x = 3)
#does not work
z_scores("my name is jeff")
#does not work
z_scores(x = c(TRUE, TRUE, FALSE, TRUE))
#does work
z_scores(x = iris)
#does not work
```

## Multiple Outputs: 
In some cases it might be better to return the mean and standard deviation instead of the Z scores. A first option is to store each of the values in a named list, and to return that list.
```{r}
mean_and_sd = function(input_x) {
  
  if (!is.numeric(x_arg)) {
    stop("Argument x should be numeric")
  } else if (length(x_arg) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
 
  mean_input = mean(input_x)
  sd_x = sd(input_x)

  list(
    mean_input = mean(input_x), 
       sd_input = sd(input_x)
  )
}
```

Storing in a data frame (uses tibble instead of list)
```{r}
mean_and_sd = function(input_x) {
  
  if (!is.numeric(x_arg)) {
    stop("Argument x should be numeric")
  } else if (length(x_arg) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
 
  mean_input = mean(input_x)
  sd_x = sd(input_x)

  tibble(
    mean_input = mean(input_x), 
       sd_input = sd(input_x)
  )
}
```

In general, either of these will be fine; which one you choose will depend on what kind of values you want to return, and what you plan to do with the function itself. If you want to return the original sample along with the computed values, a list might make sense; if you plan to run your function a lot and study the results, having a data frame will make it easier to use other tools.

## Multiple Inputs

I’d like to have a function that takes a given sample size and true simple linear regression line, simulates data from that model, and returns the estimated intercept and slope.
```{r}
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]
```

```{r}
##plotting the data generated above
sim_data %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point()
```

Making the function.
```{r}
sim_regression = function(n, beta0 = 2, beta1 = 3) {
  
  ##arguments
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )
  
  ##body
  ls_fit = lm(y ~ x, data = sim_data)
  
  ##return
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}

sim_regression(30)


sim_regression(300)
```


##Revisiting past examples
Scraped Amazon Napoleon Dynamite reviews
```{r}
read_page_reviews <- function(url) {
  
  h = read_html(url)
  
  review_titles = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  review_stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  review_text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

Next we’ll use this to read in reviews from a few pages and combine the results.
```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)

dynamite_reviews
```

Loading LoTR data: In tidy data, we broke the “only copy code twice” rule when we used the code below to process the LoTR words data:
```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = words, female:male) %>%
  mutate(race = str_to_lower(race)) %>% 
  select(movie, everything()) 
```

## Learning Assessment 1: 
Try to write a function that can be used to abstract the data loading and cleaning process. Use this function to recreate the tidied LoTR dataset.
```{r}
lotr_load_and_tidy = function(path, range, movie_name) {
  
  df = readxl::read_excel(path, range = range) %>%
    janitor::clean_names() %>%
    gather(key = sex, value = words, female:male) %>%
    mutate(race = str_to_lower(race),
           movie = movie_name)
  
  df
  
}

lotr_tidy = 
  bind_rows(
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "B3:D6", "fellowship_ring"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "F3:H6", "two_towers"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "J3:L6", "return_king")) %>%
  select(movie, everything()) 
  
```

## Functions as arguments
As a quick example, suppose we wanted to get a sense of how similar or different values in a vector are to each other. There are lots of ways to measure this – variance, standard deviation, range, inter-quartile range – and some are more appropriate in some cases than in others. The function below allows you to input a vector and a function, and returns the result of applying the specified function to the vector input.
```{r}
x = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {
  summ_func(x)
}

my_summary(x, sd)
## [1] 0.8988712
my_summary(x, IQR)
## [1] 1.271572
my_summary(x, var)
## [1] 0.8079694
```


